Assessing primitives performance\\ on multi-stage execution

### 2018-05-08 paper.tex
add small section about plugins and interpreter proxy

\cba{We need to introduce here the concept of VM plugin and interpreterproxy indirection/overhead. This is very important since later we just say this is a plugin and we don't redefine it}

>>>>

\cba{We need to introduce here the concept of VM plugin and interpreterproxy indirection/overhead. This is very important since later we just say this is a plugin and we don't redefine it}
\sk{done but someone better check what I wrote :-)}

VM plugins enable the addition of new features to the VM. There are 2 types of plugins: the built-ins and the externals. 
\begin{itemize}
\item External plugins. Plugins that can be added or removed from the VM without the need to recompile the VM sources.
\item Built-in plugins. Plugins that cannot be installed without recompiling the VM sources. However, these plugins can reach some parts of the VM internals\footnote{as data structures, routines...} that remains unreachable from an external plugin. These operations are performed via an InterpreterProxy. Although, this solution results in a substential overhead if called often.
\end{itemize}
